Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-17 PAPER.tex
JCP comments (but few edits)

\newcommand{\cc}[1]{{\color{purple} \textbf{[CC: #1]}}}
\newcommand{\acl}[1]{{\color{red} \textbf{[ACL:  #1]}}}
\newcommand{\dcj}[1]{{\color{orange} \textbf{[DCJ: #1]}}}
\newcommand{\mjk}[1]{ {\color{olive} \textbf{[MJK: #1]}} }
\newcommand{\jea}[1]{{\color{blue} \textbf{[JEA: #1]}} }

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_I.png}
\caption{The distribution of output power spectrum values for a 
given injection level P$_{in}$. The $P_{\rm out}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal. It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}). We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution. At low injection, $P_{\rm out}$ converges to the data level.}
\label{fig:Pr_vs_Pin}
\end{figure}

>>>>

\newcommand{\cc}[1]{{\color{purple} \textbf{[CC: #1]}}}
\newcommand{\acl}[1]{{\color{red} \textbf{[ACL:  #1]}}}
\newcommand{\dcj}[1]{{\color{orange} \textbf{[DCJ: #1]}}}
\newcommand{\mjk}[1]{ {\color{olive} \textbf{[MJK: #1]}} }
\newcommand{\jea}[1]{{\color{blue} \textbf{[JEA: #1]}} }
\newcommand{\jp}[1]{ {\color{pink} \textbf{[JCP: #1]}} } %y'all picked all the good colors

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_I.png}
\caption{The distribution of output power spectrum values for a 
given injection level P$_{in}$. The $P_{\rm out}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal. It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}). We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution. At low injection, $P_{\rm out}$ converges to the data level.
\jp{This figure needs updating (as does this caption).  The text seems to have settled on $P_{\rm out}$ referring to $\widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$, whereas this signal loss methodology uses only $\widehat{\textbf{p}}_{r}$.  So the y-axis needs to change.}
}
\label{fig:Pr_vs_Pin}
\end{figure}
